### 2016-04-25 ch03-lrm/nonparametric.tex
Remove PRESS figure and spectra plot

To facilitate the derivations, we rewrite the expected value of the cost function in terms of $\theta$ and $\conj{\theta}$:
\begin{align}
   \ELSCost[0]{\theta,\conj{\theta}} & =
      \frac{1}{\nWind}
           \sum_{\dW}
           \LocalModel{Q}(      \dW,        \LocalVector{\theta},  \true{      \LocalVector{Y}},  \true{      \LocalVector{U} })
           \LocalModel{Q}(\conj{\dW}, \conj{\LocalVector{\theta}}, \true{\conj{\LocalVector{Y}}}, \true{\conj{\LocalVector{U}}})
   \\
   \LocalModel{Q}(\dW, \LocalVector{\theta},  \true{\LocalVector{Y}},  \true{ \LocalVector{U} }) & \isdef
                 \LocalModel{A}(\dW, \LocalVector{\theta}) \true{\LocalVector{Y}}(\dW)
               - \LocalModel{B}(\dW, \LocalVector{\theta}) \true{\LocalVector{U}}(\dW)
               - \LocalModel{C}(\dW, \LocalVector{\theta})
    \\             
    \ELSCost[n]{\theta,\conj{\theta}} & =
              \frac{\sigma_V^2}{\nWind} 
                     \sum_{r} 
                               \LocalModel{A}(      \dW,        \LocalVector{\theta} ) 
                               \LocalModel{A}(\conj{\dW}, \conj{\LocalVector{\theta}}) 
\end{align}
since $\conj{ \LocalModel{A}(\dW,\theta)} =  \LocalModel{A}(\conj{\dW},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.

@@

In the simulations, we consider a discrete-time second order system with transfer function
\begin{equation}
\true{G}(z) = \frac{0.64587 z + 0.64143}
                                      {47.9426 z^2 - 51.2955 z + 46.9933}
                                      \text{,}
\end{equation}
this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$, $\damping=0.05$.
The system is scaled such that its peak amplitude is $3\unit{dB}$ and hence its $3\unit{dB}$ bandwidth can be read easily from bode plots.
As indicated in \figref{fig:nparam:blockH0}, the noise filter $\true{H}' = 1$ is used such that white noise is disturbing the output.
The gain $\kappa$ of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int\limits_{\BW} \powerspec{\true{Y}}(\omega) \dd\omega}
            {\int\limits_{\BW} \powerspec{V}(\omega) \dd{\omega}}
  % \frac{\int_{\BW} \abs{\true{Y}(\omega)}^2 \dd{\omega}}
  %           {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\powerspec{\bullet}$ denotes the \gls{PSD} of $\bullet$ and $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to \[
\SNR_{\BW} \in \set{10, 20, 40, 60, \infty} \unit{dB}\text{.}
\]

@@

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOtikzfig[figure with G and errors for 1 simulation]
  \caption[Estimated FRF using local modeling]{The figure shows the \gls{FRF} of a single simulation for $\SNR= 40 \unit{dB}$ and $\nBW =  64$, together the the error ($\model{\bullet} - \true{G}$) for the different methods. The $3\unit{dB}$ bandwidth of the system is highlighted.}
\end{figure}

We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over $\nMC=\num{2000}$ Monte Carlo runs of the simulations above.
Specifically, the following values
\begin{align}
  \sampleMean{\bullet}(\omega_k) & 
  \isdef
    \frac{1}{\nMC}
    \sum_{i=1}^{\nMC}
    \model[\atSimulation{i}]{\bullet}(\omega_k)
  \\
  \sampleBias{\bullet}(\omega_k) &
    \isdef
    \frac{1}{\nMC}
    \sum_{i=1}^{\nMC}
    \model[\atSimulation{i}]{\bullet}(\omega_k) - \true{G}(\omega_k)
    = 
    \sampleMean{\bullet}(\omega_k) - \true{G}(\omega_k)
    \\
    \sampleVariance{\bullet}(\omega_k) &
    \isdef
    \frac{1}{\nMC - 1}
    \sum_{i=1}^{\nMC}
                   \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right)
    \conj { \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \true{G}(\omega_k) \right) }
    \\
    \RMSE_{\bullet}(\omega_k) & \isdef \sqrt{\sampleVariance{\bullet}(\omega_k) + \sampleBias{\bullet}^{2}(\omega_k)}
\end{align}
are computed and are the sample estimates of respectively the expected value $\E{\model{\bullet}}$, bias $\bias{\model{\bullet}}$ and variance $\Var{\model{\bullet}}$ of the model.
Remark, that the standard deviation on the $\sampleBias{\bullet} \approx \sqrt{\sampleVariance{\bullet} / \nMC}$ which limits the precision with which we can hence observe $\sampleBias{\bullet}$. 
For $\nMC=\num{2000}$, this means that we can detect the bias only when it is at most $20 \log \sqrt{\num{2000}} \unit{dB} \approx 33 \unit{dB}$ smaller than $\sampleStd{\bullet}$ and smaller biasses cannot be detected by the simulations.

@@

\begin{figure}
  \centering
  \remakeNextFigure
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system which has been highlighted.}
  \label{fig:nparam:mc:singleTuple}
\end{figure}

@@

\paragraph{Poor signal-to-noise ratios}
In \figref{fig:nparam:comparison:lowSNR} and \figref{fig:nparam:comparison:terribleSNR}, the results are shown for $\SNR=20\unit{dB}$ and $\SNR=10\unit{dB}$ respectively.
Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
The

@@

Note that since the \gls{PRESS} can be interpreted similar to the residuals, this forms a convenient metric to select models on.
In particular, when there is a large difference between the residuals and the \gls{PRESS}, this indicates that a poor model has been selected.

\begin{figure}
  \centering
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \TODOtikzfig[PRESS and noise for single simulation]
  \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the variance of the residuals and the \glsentrytext{PRESS} statistic to select a good local model.}
  \label{fig:nparam:PRESS}
\end{figure}

>>>>

To facilitate the derivations, we rewrite the expected value of the cost function in terms of $\theta$ and $\conj{\theta}$:
\begin{align}
   \ELSCost[0]{\theta,\conj{\theta}} & =
      \frac{1}{\nWind}
           \sum_{\dW}
           \LocalModel{Q}(      \dW,        \LocalVector{\theta},  \true{      \LocalVector{Y}},  \true{      \LocalVector{U} })
           \LocalModel{Q}(\conj{\dW}, \conj{\LocalVector{\theta}}, \true{\conj{\LocalVector{Y}}}, \true{\conj{\LocalVector{U}}})
   \\
   \LocalModel{Q}(\dW, \LocalVector{\theta},  \true{\LocalVector{Y}},  \true{ \LocalVector{U} }) & \isdef
                 \LocalModel{A}(\dW, \LocalVector{\theta}) \true{\LocalVector{Y}}(\dW)
               - \LocalModel{B}(\dW, \LocalVector{\theta}) \true{\LocalVector{U}}(\dW)
               - \LocalModel{C}(\dW, \LocalVector{\theta})
    \\             
    \ELSCost[n]{\theta,\conj{\theta}} & =
              \frac{\sigma_V^2}{\nWind} 
                     \sum_{\delta} 
                               \LocalModel{A}(      \dW,        \LocalVector{\theta} ) 
                               \LocalModel{A}(\conj{\dW}, \conj{\LocalVector{\theta}}) 
\end{align}
since $\conj{ \LocalModel{A}(\dW,\theta)} =  \LocalModel{A}(\conj{\dW},\conj{\theta}) $, and similar for $\LocalModel{B}$ and $\LocalModel{C}$ and $\LocalModel{Q}$.

@@

In the simulations, we consider a discrete-time second order system with transfer function
\begin{equation}
\true{G}(z) = \frac{0.64587 z + 0.64143}
                                      {47.9426 z^2 - 51.2955 z + 46.9933}
                                      \text{,}
\end{equation}
this is a resonant system with a resonance near $\omega=1\unit{rad/sample}$, $\damping=0.05$.
The system is scaled such that its peak amplitude is $3\unit{dB}$ and hence its $3\unit{dB}$ bandwidth can be read easily from bode plots.
As indicated in \figref{fig:nparam:blockH0}, the noise filter $\true{H}' = 1$ is used such that white noise is disturbing the output.
The gain $\kappa$ of this filter is adapted such that the \gls{SNR} in the $3\unit{dB}$ bandwidth of the system, i.e.
\begin{equation}
  \SNR_{\BW} \isdef
  \frac{\int\limits_{\BW} \powerspec{\true{Y}}(\omega) \dd\omega}
            {\int\limits_{\BW} \powerspec{V}(\omega) \dd{\omega}}
  % \frac{\int_{\BW} \abs{\true{Y}(\omega)}^2 \dd{\omega}}
  %           {\int_{\BW} \abs{V(\omega)}^2 \dd{\omega}}
\end{equation}
where $\powerspec{\bullet}$ denotes the \gls{PSD} of $\bullet$ and $\BW$ is the $3 \unit{dB}$ bandwidth of the system, is fixed to \[
\SNR_{\BW} \in \set{10, 20, 40, 60, \infty} \unit{dB}\text{.}
\]
This ensures that the excited bins in the $3\unit{dB}$ bandwidth of the system each receive a pre-defined \gls{SNR}.

@@

% \begin{figure}
%   \centering
%   \setlength{\figurewidth}{0.85\columnwidth}
%   \setlength{\figureheight}{0.62\figurewidth}
%   \TODOtikzfig[figure with G and errors for 1 simulation]
%   \caption[Estimated FRF using local modeling]{The figure shows the \gls{FRF} of a single simulation for $\SNR= 40 \unit{dB}$ and $\nBW =  64$, together the the error ($\model{\bullet} - \true{G}$) for the different methods. The $3\unit{dB}$ bandwidth of the system is highlighted.}
% \end{figure}

We then compute basic statistics of the estimated \glspl{FRF} $\model[\atSimulation{i}]{\bullet}$ over $\nMC=\num{2000}$ Monte Carlo runs of the simulations above.
Specifically, the following values
\begin{align}
  \sampleMean{\bullet}(\omega_k) & 
  \isdef
    \frac{1}{\nMC}
    \sum_{i=1}^{\nMC}
    \model[\atSimulation{i}]{\bullet}(\omega_k)
  \\
  \sampleBias{\bullet}(\omega_k) &
    \isdef
    \frac{1}{\nMC}
    \sum_{i=1}^{\nMC}
    \model[\atSimulation{i}]{\bullet}(\omega_k) - \true{G}(\omega_k)
    = 
    \sampleMean{\bullet}(\omega_k) - \true{G}(\omega_k)
    \\
    \sampleVariance{\bullet}(\omega_k) &
    \isdef
    \frac{1}{\nMC - 1}
    \sum_{i=1}^{\nMC}
                   \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \sampleMean{\bullet}(\omega_k) \right)
    \conj { \left({\model[\atSimulation{i}]{\bullet}}(\omega_k) - \sampleMean{\bullet}(\omega_k) \right) }
    \\
    \RMSE_{\bullet}(\omega_k) & \isdef \sqrt{\sampleVariance{\bullet}(\omega_k) + \sampleBias{\bullet}^{2}(\omega_k)}
\end{align}
are computed and are the sample estimates of respectively the expected value $\E{\model{\bullet}}$, bias $\bias{\model{\bullet}}$ and variance $\Var{\model{\bullet}}$ of the model.
Remark, that the standard deviation on the $\sampleBias{\bullet} \approx \sqrt{\sampleVariance{\bullet} / \nMC}$ which limits the precision with which we can hence observe $\sampleBias{\bullet}$. 
For $\nMC=\num{2000}$, this means that we can detect the bias only when it is at most $20 \log \sqrt{\num{2000}} \unit{dB} \approx 33 \unit{dB}$ smaller than $\sampleStd{\bullet}$ and smaller biasses cannot be detected by the simulations.

@@

\begin{figure}
  \centering
  \remakeNextFigure
  \setlength{\figurewidth}{0.85\columnwidth}
  \setlength{\figureheight}{0.62\figurewidth}
  \input{\thisDir/figs/MC-SNR40-NBW64and8.tikz}
  \caption[Bias, variance for $\nBW\in{8,64}$ at $\SNR=40\unit{dB}$]{The bias, variance and \gls{RMS} error of the different estimators is shown for $\SNR= 40 \unit{dB}$ and $\nBW \in \set{8,64}$ samples in the $3 \unit{dB}$ bandwidth of the system (as highlighted).}
  \label{fig:nparam:mc:singleTuple}
\end{figure}

@@

\paragraph{Poor signal-to-noise ratios}
In \figref{fig:nparam:comparison:lowSNR} and \figref{fig:nparam:comparison:terribleSNR}, the results are shown for $\SNR=20\unit{dB}$ and $\SNR=10\unit{dB}$ respectively.
Again, it can be seen that \gls{LRIC} is plagued by high variance and is hence not directly usable.
At $\SNR=20\unit{dB}$ the \gls{LPM} and the \gls{LRM} is significantly biased for small datasets ($\nBW < 6$), however, the \gls{LRM} still perform better than the \gls{LPM}.
For larger datasets ($\nBW \geq 16$), all methods perform similarly and at a nearly constant level of (variance) error.
The \gls{LRM}, in contrast to the \gls{LPM}, still contains an observable bias in the simulations.
At even lower $\SNR=10\unit{dB}$,  most methods perform quite poorly for short datasets ($\nBW < 6$).
However, here it can be seen that the $\lpm{7,4,4}$ outperforms both the $\lrm{7,1,1,1}$ and $\lrm{7,2,2,2}$ and slightly worse than $\lrm{6,2,2,2}$.
It can be seen that the bias error of the \gls{LPM} drops off more quickly ($\bigO{\nBW^{-3}}$) than the \gls{LRM} bias which drops in approximately $\bigO{\nBW^{-1}}$.

@@

Note that since the \gls{PRESS} can be interpreted similar to the residuals, this forms a convenient metric to select models on.
In particular, when there is a large difference between the level of the residuals and the \gls{PRESS}, this indicates that a poor model has been selected.

% \begin{figure}
%   \centering
%   \setlength{\figurewidth}{0.85\columnwidth}
%   \setlength{\figureheight}{0.62\figurewidth}
%   \TODOtikzfig[PRESS and noise for single simulation]
%   \caption[Output spectrum for local modeling, together the PRESS statistic]{It is convenient to compare the variance of the residuals and the \glsentrytext{PRESS} statistic to select a good local model.}
%   \label{fig:nparam:PRESS}
% \end{figure}
